### 2023-10-29 generalExploration.Rmd
explicit logging test (#3)

tstep=1000
popsize=c()
popsum=list()
for(time in 1:tstep){
    print(paste("------",time,"------"))
    for(i in sample(1:length(population))){
        ind=tryCatch(population[[i]]$id,error=function(e)NULL)
        if(!is.null(ind)){
            ##ageing

@@

            ##repro
            partner=population[[ind]]$partner
            canrepro=population[[ind]]$repro
            if(partner>0 & !canrepro){
                #print(paste("childtest",ind,partner,population[[ind]]$community,population[[partner]]$community))
                population[[partner]]$repro=TRUE #make sure proba of reproduction is unique for all pair 
                ad_tr=initcomus$adaptivetraits[population[[ind]]$community,]
                lambda=b+r*sum(ad_tr)
                nchild=rpois(1,lambda)
                if(nchild>0){
                    for(i in 1:nchild){
                        print("newborn")
                        newborn=reproduction(population[[ind]],population[[partner]],neutraltraitsParam,population[[length(population)]]$id)
                        population[[newborn$id]]=newborn
                        initcomus$size[newborn$community]=initcomus$size[newborn$community]+1
                    }
                }
            }
            population[[ind]]$repro=FALSE

@@

                        print(paste("marriage",ind,partner,"moving all to",jc," and leaving",lc, ",new:" ,population[[partner]]$community,population[[ind]]$community))
                    }
                }
            }

            #Handle deaths
            if(runif(1)<d){
                if(partner>0) population[[partner]]$partner=-1
                initcomus$size[population[[ind]]$community]=initcomus$size[population[[ind]]$community]-1
                population[[ind]]=NULL
                print(paste("dead ind",ind))
            }
        }

@@

        #quickly summarize
        popsum[[time]]=sapply(names(population[[1]]),function(n)table(sapply(population,"[[",n)))
        ##
        plot(initcomus$coordinates,pch=21,bg=apply(initcomus$adaptivetraits,1,mean)+1,cex=log(initcomus$size))
        popsize=c(popsize,length(population))
    }
    ## Fission
    overloaded=initcomus$size>Th
    if(sum(overloaded)>0){
        for(split in which(overloaded))
            print(paste("community",split,"with size",initcomus$size[split]))
        #        for(split in which(overloaded))

>>>>

tstep=1000
popsize=c()
popsum=list()
for(time in 1:tstep){
    if(logging=="time")print(paste("------",time,"------"))
    for(i in sample(1:length(population))){
        ind=tryCatch(population[[i]]$id,error=function(e)NULL)
        if(!is.null(ind)){
            ##ageing

@@

            ##repro
            partner=population[[ind]]$partner
            canrepro=population[[ind]]$repro
            if(partner>0 & !canrepro){
                if(logging=="verbose")print(paste("childtest",ind,partner,population[[ind]]$community,population[[partner]]$community))
                population[[partner]]$repro=TRUE #make sure proba of reproduction is unique for all pair 
                ad_tr=initcomus$adaptivetraits[population[[ind]]$community,]
                lambda=b+r*sum(ad_tr)
                nchild=rpois(1,lambda)
                if(nchild>0){
                    for(i in 1:nchild){
                        newborn=reproduction(population[[ind]],population[[partner]],neutraltraitsParam,population[[length(population)]]$id)
                        if(logging=="demo")print(paste("newborn in ",newborn$community))
                        population[[newborn$id]]=newborn
                        initcomus$size[newborn$community]=initcomus$size[newborn$community]+1
                    }
                }
            }
            population[[ind]]$repro=FALSE

@@

                        if(logging=="pairing")print(paste("marriage",ind,partner,"moving all to",jc," and leaving",lc, ",new:" ,population[[partner]]$community,population[[ind]]$community))
                    }
                }
            }

            #Handle deaths
            if(runif(1)<d){
                if(partner>0) population[[partner]]$partner=-1
                initcomus$size[population[[ind]]$community]=initcomus$size[population[[ind]]$community]-1
                if(logging=="demo") print(paste("dead ind",ind,"in",population[[ind]]$community))
                population[[ind]]=NULL
            }
        }

@@

        #quickly summarize
        popsum[[time]]=sapply(names(population[[1]]),function(n)table(sapply(population,"[[",n)))
        ##
        plot(initcomus$coordinates,pch=21,bg=apply(initcomus$adaptivetraits,1,mean)+1,cex=log(initcomus$size))
        popsize=c(popsize,length(population))
    }

    ## Fission
    overloaded=initcomus$size>Th
    if(sum(overloaded)>0){
        for(split in which(overloaded))
            print(paste("community",split,"with size",initcomus$size[split]))
        #        for(split in which(overloaded))
